Supporting Information

### 2018-02-21 SupportingInformation.Rmd
mostly changes to implement the bivariate models selection on Terry's C/N data, and to randomize copula structure and see what it does to the distribution of some ecosystem function
a few changes to the structure of supporting information so it can show all the analyses we performed in the same structure as the paper outline

# Testing the ranking and bivariate copula display function

This is just for testing the `getcopula` function.

@@

# Testing the bivariate model selection and goodness-of-fit pipeline

This is just for testing the `OurBiCopSelect` function. We test that
it runs and gives reasonable results by simulating data and seeing if 
you recover what kind of copula was used.

@@

If real data come from a Clayton copula, independence should
be rejected, Clayton should be the AIC best, it should pass the
goodness of fit test, and the normal copula should fail the
goodness of fit test:
<!--Test for real data from a clayton-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,seed,mtime("OurBiCopSelect.R"))}
set.seed(seed)

@@

#data are really from a clayton
cop<-claytonCopula(5,2)
dat<-rCopula(numdat,cop)
allresC<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresC
```

@@

#data are really from a gumbel
cop<-gumbelCopula(6,2)
dat<-rCopula(numdat,cop)
allresG<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresG
```

@@

#data are really from a frank
cop<-frankCopula(5,2)
dat<-rCopula(numdat,cop)
allresF<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresF
```

@@

#data are really from a joe
cop<-joeCopula(6,2)
dat<-rCopula(numdat,cop)
allresJ<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresJ
```

The goodness of fit test is quite slow when testing the fit of a
normal copula, and the results are not great: often the normal copula
cannot be rejected even when it is not the true copula, even though
a comparison of A/BICs strongly supports the true copula over the normal.
So I think the best way forward is to use `gofnormal=FALSE`.

# Testing the pipeline for examining tail dependence in bivariate data

>>>>

# Question 1 analyses for each dataset

# Question 2 analyses for each dataset

# Question 3 analyses for each dataset

# Testing

## Testing the ranking and bivariate copula display function

This is for testing the `getcopula` function.

@@

## Testing the bivariate model selection and goodness-of-fit pipeline

This is for testing the `OurBiCopSelect` function. We test that
it runs and gives reasonable results by simulating data and seeing if 
you recover what kind of copula was used.

@@

If real data come from a Clayton copula, independence should
be rejected, Clayton should be the AIC best, it should pass the
goodness of fit test, the normal copula should fail the
goodness of fit test, and model-averaged tail dependence should
indicate left-tail dependence:
<!--Test for real data from a clayton-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,seed,mtime("OurBiCopSelect.R"))}
set.seed(seed)

@@

#data are really from a clayton
cop<-claytonCopula(5,2)
dat<-rCopula(numdat,cop)

#do the analysis
allresC<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresC

#calculate model-averaged left- and right-tail dependence
#DAN: ad this later
```

@@

#data are really from a gumbel
cop<-gumbelCopula(6,2)
dat<-rCopula(numdat,cop)

#do the analysis
allresG<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresG

#calculate model-averaged left- and right-tail dependence
#DAN: ad this later
```

@@

#data are really from a frank
cop<-frankCopula(5,2)
dat<-rCopula(numdat,cop)

#do the analysis
allresF<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresF

#calculate model-averaged left- and right-tail dependence
#DAN: ad this later
```

@@

#data are really from a joe
cop<-joeCopula(6,2)
dat<-rCopula(numdat,cop)

#do the analysis
allresJ<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresJ

#calculate model-averaged left- and right-tail dependence
#DAN: ad this later
```

The goodness of fit test is quite slow when testing the fit of a
normal copula, and the results are not great: often the normal copula
cannot be rejected even when it is not the true copula, even though
a comparison of A/BICs strongly supports the true copula over the normal.
So proceed using `gofnormal=FALSE` when analyzing real data.

# Testing the pipeline for examining tail dependence in bivariate data using `copsurrog2d`
